\chapter{Acknowledgements}

The four years that I worked on this thesis were without a doubt the most challenging and transformative of my adult life. I like to think that I have come out stronger and wiser, but this is hardly to my own credit. As such, I have a large list of people to thank:

Firstly, my promotor \textbf{Martin Herold}, Shrewd Strategic Sage of Spatial Science, for providing exactly the right words and ideas at exactly the right moments. I hope to one day reach a level of wisdom and insight that lets me do the same, and pay it forward.

The relentless \textbf{Tomislav Hengl}, Meritous Mad Mapper of Mayhem, whose bottomless drive and energy are the the primary reason I even did all this. I hope to keep butting heads, ideas, and cups with you for years to come.

The sagacious \textbf{Sytze de Bruin}, Merciless Masticator of my Many Mistakes. I vividly remember the first time I came to him for advice on my MSc thesis: His capacity for good advice and tough, but constructive criticism has been a continuous boon to everything I've written since. May the scorching glare of his unsalted criticism keep perfecting all he beholds.

The impressive \textbf{Leandro Parente}, Meticulous Master of Music, Meat, and Many Methods, for sharing his technical expertise, level head, and professional perspectives, and of course for blasting his beautiful beats.

Honorary supervisor, \textbf{Ichsani Wheeler}, Energetic Eater of Elephants. I would not have finished this thesis without her guidance, mental support, babysitting, gyoza, tough love, deadlines, reminders of meaning, and unlimited cheerful banter.

My Precious Paranymphs, Dainius Masili\={u}nas and Xuemeng Tian, Both Bright Brainiacs Facing Fantastic Futures. Dainius, the absolute smartest and most lovable person at GRS, was there when I started my GIS master's many years ago, and I am proud to have him at my side during my defense and all its preparations. I have not known Xuemeng equally long, but the two years that we have shared at OpenGeoHub have been filled with excellent dinners and conversations, and her perspective and mindset never cease to inspire me. I am supremely thankful to them both for chasing and motivating me to sort out the defense, despite their own daunting deadlines.

\textbf{Rolf Simoes}, Zestful Zen Zealot of Zenodo, whose help, advice, and indestructible optimism made the last stressful months and hours bearable, and with whom I hope to collaborate for years to come.

\textbf{Maya Kroodsma}, Expedient Editor Extraordinaire and Erstwhile Eega. I am infinitely grateful to her for finding truth in all aspects of my life, and, more tangibly, for the immense amount of mental, logistical and editorial support during the writing of this thesis. These last four years have been an intense journey for us. However, if journeys are really about the friends you make along the way, I can count myself singularly fortunate to have made such a formidable friend.

\textbf{Carsten Lygteskov Hansen}, Benevolent Blackbeard and Beer Buddy, whose advice, encouragement and mentorship got me both into and through this mess.

\textbf{Luka Antonic}, Coolest Co-author and Courageous Co-host, for being there at 2AM, whether writing about Sentinel-2 resampling, giving me gratuitous goulash, twerking to turbofolk, or smashing spaceships to smithereens.

All the wonderful people at \textbf{OpenGeoHub}, past and present, for the savage (after)parties, sword fights, glass-shattering barbecues, dangerous delicacies, epically cutthroat game nights (and mornings), road trips, cookie rounds, and endless laughter.

Most notably, \textbf{Carmelo Bonannella}, Charming Buccaneer of Freezing Forests and Majestic Mountains, a 'PhD Twin' whose erudition dwarfs my own, and whose will and fortitude I can only dream of approximating. I always enjoy realizing how much we have in common despite being so different. Thank you being the best Blue Oni I could have wished for.

Last but not least, \textbf{Ron van Lammeren}, for making my first encounters with spatial analysis such a positive experience by means of his seemingly infinite time, memory and affection for all GIS students. 